---
title: "Getting Started with t4stats"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started with t4stats}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
  knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Overview

`t4stats` computes **four** statistics from a numeric vector:

-   **Function A (C++)**: Sample variance (unbiased, divides by *n − 1*)
-   **Function B (C++)**: Arithmetic mean
-   **Mean (R)**: `mean(x)`
-   **Variance (R)**: `stats::var(x)`

A single helper, `run_all(x)`, prints all four results and returns them in a list.

```{r}
   library(t4stats)

```

## Basic Example

```{r, eval=FALSE}
   x <- c(1, 2, 3, 4, 5)
   out <- run_all(x)   # prints 4 lines and returns a list invisibly
   str(out)
```

## You should see that

-   `out$A` equals `out$Variance` (both are sample variance)
-   `out$B` equals `out$Mean`

```{r, eval=FALSE}
   all.equal(out$A, var(x))
   all.equal(out$B, mean(x))
```

## Using your own data

If you ship a CSV with the package, put it under `inst/extdata/`. Then access it like this:

```{r, eval=FALSE}
   csv_path <- system.file("extdata", "Data501_Dataset_Assignment1.csv", package = "t4stats")
   dat <- read.csv(csv_path, header = TRUE)
   x <- as.numeric(dat[[1]]) + 563      # example offset from the assignment
   run_all(x)
```

> **Tip:** Don’t keep data at the top level of the package—`R CMD check` will note it. Prefer storing it under `inst/extdata/`.

## What each function does

```{r, eval=FALSE}
   mean_R(1:5)       # R mean
   variance_R(1:5)   # R sample variance

   # C++ implementations are called inside run_all(), but are also available:
   t4stats:::my_function_A(1:5)  # variance in C++
   t4stats:::my_function_B(1:5)  # mean in C++
```


-   `my_function_A()` uses the unbiased sample variance formula:\
    ∑(xᵢ − x̄)² / (n − 1)\
-   `my_function_B()` computes the arithmetic mean:\
    (1 / n) ∑ xᵢ

## Reproducibility notes

-   Adding a constant to all values changes the mean but not the variance.\
-   `run_all()` prints the four lines in the assignment’s format:
    -   “Function A Results: …”\
    -   “Function B Results: …”\
    -   “Mean: …”\
    -   “Variance: …”

## Installation (from source)

```{r, eval=FALSE}
   # from the package root
   devtools::document()
   devtools::build()
   devtools::install()
   library(t4stats)
```


## Session info

```{r, eval=FALSE}
   sessionInfo()
```
